%====================================================================================================
\begin{abstractpage}{Disclaimer}
%====================================================================================================
The method used to search for \BKnn decays presented in this thesis was co-designed by my supervisor Dr.~Alexander Glazov (AG), my colleagues Filippo Dattola (FD), Dr.~Simon Kurz (SK), Dr.~Slavomira Stefkova ($\mathrm{S^2}$), and myself.

I was involved in every step of the analysis, and I carried out the entirety of the search for \BKpnn and \BKznn decays presented in this thesis with the dataset of $\lumion$.
All the code developed for this analysis was either written or reviewed by me, and I am the author of the shown figures in this thesis, unless specified otherwise. In particular:
\bi
\item The code employed for the validation channel (\cref{sec:jpsi}) was co-written by SK, AG, FD, and myself.
\item The code to produce \cref{fig:form_factor,,fig:yield_stability,,fig:63_mu_uncertainty} (right) was written by AG.
\item The code of the simplified Gaussian model (\cref{fig:limit_expectation,fig:63_fit_pulls}) was implemented by AG, and validated by AG, $\mathrm{S^2}$, and myself.
\item The code to classify the background sources (\cref{ch:appendix_bkg_composition}) and to plot the binned expected signal selection efficiency (\cref{fig:signal_efficiency_q2}) was written by FD.
\item The code to compute the systematic uncertainties (\cref{sec:systematics}) was co-written by AG, FD, and myself.
\item The code to apply and validate the maximum-likelihood fit, and to produce \cref{fig:63_post_fit,fig:63_limit_on_br}, was co-written by $\mathrm{S^2}$, SK, FD, and myself.
\ei

The result obtained with a first iteration of the method on a restricted dataset of \lumionpartial (\cref{sec:first_iteration}) is shared between this thesis and the thesis of FD, and was published in the Physical Review Letters in October 2021 \cite{Belle-II:2021rof}.
The published article was co-written by FD, AG, SK, $\mathrm{S^2}$, and myself.

My contribution to other publications that I co-authored with the Belle II tracking group \cite{Bertacchi2021} or the Belle II collaboration \cite{Belle-II:2019usr,Belle-II:2019qfb,Belle-II:2020jti,Belle-II:2021cxx,Belle:2021efh} during my doctoral studies are not covered by this thesis.

%====================================================================================================
\end{abstractpage}
%====================================================================================================
\begin{abstractpage}{Acknowledgments}
%====================================================================================================
I would like to express my gratitude to the SuperKEKB group and the Belle II collaboration without which this project would not have been possible;
to my thesis supervisor Sasha Glazov for his continuous support, his enthusiasm, and the hours that he did not count to share his knowledge and insights;
to my working group colleagues Filippo Dattola, Eldar Ganiev, Simon Kurz, and Slavomira Stefkova, for the time spent together in Europe and in Japan, the fruitful discussions, and their helpful comments on the draft of my thesis;
to Carsten Niebuhr, for his support and for offering me the opportunity to work in a team that I will miss;
to my co-supervisor Kerstin Tackmann, who found the time to follow my thesis;
to Adrien Florio, Michael de Nuccio, Navid Rad, Clara Flintrop, and Vlad Popescu for their helpful comments on the draft of my thesis;
to my other colleagues at DESY, in particular Henrikas Svidras, Abtin Narimani, Sascha Dreyer, Anselm Baur, Tommy Martinov, Lorenzo Quintavalle, and Philipp Tontsch, for making me feel less alone on the PhD path;
to my family and my parents, for their continuous support;
to Dolma, for most of the reasons above, and too many others.

%====================================================================================================
\end{abstractpage}
%====================================================================================================
\begin{abstractpage}{Declaration}
%====================================================================================================

I hereby declare upon oath that I have written the present dissertation independently and have not used further resources and aids than those stated in the dissertation.

\textit{Hiermit erkläre ich an Eides statt, dass ich die vorliegende Dissertationsschrift selbst verfasst und keine anderen als die angegebenen Quellen und Hilfsmittel benutzt habe.}
\par\bigskip
\par\bigskip

\begin{flushright}
\par\bigskip
\textbf{Cyrille Praz}\\
\textbf{Hamburg, the 29th of August 2022}
\end{flushright}
%====================================================================================================
\end{abstractpage}
%====================================================================================================
